|

### 2023-10-25 paper/paper.qmd
Translate Acknowledgements

## Acknowledgements {#acknowledgements .appendix}

Many thanks to Stefano De Pascale for his countless suggestions on how to improve this article. My thanks also go to Manon Buysse and Julie Nijs for proofreading this article. Any remaining errors are, of course, my own.

>>>>

## Dankwoord {#acknowledgements .appendix}

Veel dank aan Stefano De Pasale voor zijn talloze suggesties om dit artikel te verbeteren. Mijn dank gaat ook uit naar Manon Buysse en Julie Nijs, die dit artikel hebben nagelezen. Enige resterende fouten zijn, uiteraard, die van mij.
